---
title: "A3: SPL Library Checkouts"
output: html_document
---

### Introduction

The analysis is about the trends of the five material types including Atlas, Audio book, Book, E-book, and Videodisc. It is really important to analyze the trends over time because it represents the preference of the reader. Moving with trends will lead to profit for the publishers and authors. What has happened in the past years gives an idea of what will happen in the future. The analysis will show the reader's preference of the books' types in each year and each month. The material type of books will be compared with the number of checkouts as well. 

### Summary Information



### The Dataset

- Who collected/published the data?  
The data was published by the Seattle Public Library. 
- What are the parameters of the data (dates, number of checkouts, kinds of books, etc.)?
The parameters of the data are UsageClass, CheckoutType MaterialType, CheckoutYear, CheckoutMonth, Checkouts, Title, ISBN, Creator, Subjects, Publisher, and PublicationYear. 
- How was the data collected or generated?  
The data was collected by the Seattle Public library. The data is categorized by the different parameters, which also contains information about how the different books have been checkouted throughout the years of 2022 and 2023.  
- Why was the data collected?  
The data was collected to see the different trends of books over time. The data allows the publisher and author 
to know what kinds of books are more popular than the others and how many books got borrowed on a specific date. It also helps the system to keep track about the books at the library.
- What, if any, ethical questions do you need to consider when working with this data?

- What are possible limitations or problems with this data?   (at least 200 words)
There are some possible limitations with this data. 

### First Trends Over Time Chart

Include a chart. Make sure to describe why you included the chart, and what patterns emerged

The first chart that you will create and include will show the trend over time of your variable/topic/interest. Think carefully about what you want to communicate to your user (you may have to find relevant trends in the dataset first!). Here are some requirements to help guide your design:

- Show more than one, but fewer than ~10 trends
  - For example, two books, or 5 different mediums
- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear - legend title
In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

When we say "clear" or "human readable" titles and labels, that means that you should not just display the variable name.

Here's an example of how to run an R script inside an RMarkdown file:

``````{r, echo = FALSE, warning = FALSE, code = readLines("chart1_example.R")}
```

### Second Trends Over Time Chart

Include a chart. Make sure to describe why you included the chart, and what patterns emerged

The second chart that you will create and include will show another trend over time of your variable/topic/interest. Think carefully about what you want to communicate to your user (you may have to find relevant trends in the dataset first!). Here are some requirements to help guide your design:

- Show more than one, but fewer than ~10 trends
  - For example, two books, or 5 different mediums
- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear - legend title
In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

When we say "clear" or "human readable" titles and labels, that means that you should not just display the variable name.

Here's an example of how to run an R script inside an RMarkdown file:

``````{r, echo = FALSE, code = readLines("chart2_example.R")}
```

### Your Choice

The last chart is up to you. It could be a line plot, scatter plot, histogram, bar plot, stacked bar plot, and more. Here are some requirements to help guide your design:

- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear legend title

Here's an example of how to run an R script inside an RMarkdown file:

``````{r, echo = FALSE, code = readLines("chart2_example.R")}
```


